Bootstrap Confidence Intervals for Regression Discontinuity Designs with Uniform Kernels

### 2016-02-21 main_paper.tex
Make minor formatting and notation changes to paper

\begin{assumption}[Bandwidth]\label{A3}
Let $h_n$ be the bandwidth used to estimate the local polynomial of order $p$ and let $b_n$ be the bandwidth used for $p+1$. Then $h_n$, $b_n = o(n^{-1/5})$,
$n h_n$, $n b_n \to \infty$ as $n \to \infty$, and $h_n \leq b_n$ for all $n$.\footnote{Unless otherwise stated, all limits in this paper are assumed to hold as $n \to \infty$.}
\end{assumption}

@@

\begin{algorithm}[Bias estimation]\label{Alg1}
  Assume $h_n$ and $b_n$ are bandwidths as described by Assumption~\ref{A3} and
  define
  \begin{align}
    I^-(h) &= \{i : h < X_i < 0\}, &
    I^+(h) &= \{i : 0 < X_i < h\}.
  \end{align}
  Also define $M^-(h_n)$ and $M^+(h_n)$ to be the number of elements in
  $I^-(h_n)$ and $I^+(h_n)$ respectively.
  \begin{enumerate}
  \item Estimate the local polynomials $g_{p+1}^+$ and $g_{p+1}^-$ as defined by
    Equation --- and define the residuals
    \begin{equation}
      \label{eq:1}
      \hat\varepsilon_i =
      \begin{cases}
        Y_i - \hat g_{p+1}^-(X_i) & \textif\ X_i < 0 \\
        Y_i - \hat g_{p+1}^+(X_i) & \otherwise
      \end{cases}
    \end{equation}
  \item Repeat the following steps $B_1$ times to produce a sequence of bootstrap
    estimates $\hat\tau_1^*,\dots,\hat\tau_{B_1}^*$. For the $k$th step:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M^-(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^-(b_n)\}$ and one of size $M^+(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^+(h_n)\}$. Let $\varepsilon_i^{*-}$ and
      $\varepsilon_i^{*+}$ denote the $i$th element of each sample and construct
      \begin{align}
        \label{eq:2}
        Y_i^{*-} &= \hat g_{p+1}^-(X_i^{*-}) + \varepsilon_i^{*-} &
        Y_i^{*+} &= \hat g_{p+1}^+(X_i^{*+}) + \varepsilon_i^{*+}
      \end{align}
    \item Calculate $\hat\mu_+^*$ and $\hat\mu_-^*$ as
      \begin{align}
        \hat\mu_-^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^-(h_n)} (Y_i^{*-} -
          (\beta_0 + \beta_1 X_i^{*-} + \cdots + \beta_p (X_i^{*-})^p))^2 \\
        \hat\mu_+^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^+(h_n)} (Y_i^{*+} -
          (\beta_0 + \beta_1 X_i^{*+} + \cdots + \beta_p (X_i^{*+})^p))^2
      \end{align}
    \item Save $\hat\mu_+^* - \hat\mu_-^*$ as $\hat\tau^*_k$.
    \end{enumerate}
  \item Calculate the bias estimator as
    \begin{equation}
      \label{eq:4}
      \hat\Delta = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k -
      \big[\hat g_{p+1}^+(0) - \hat g_{p+1}^-(0)\big]
    \end{equation}
  \end{enumerate}
\end{algorithm}
Obviously, the distribution of $\hat\Delta$ depends on $B_1$ and we could
incorporate that dependency into our notation by wrting
$\hat\Delta_{B_1}$. However, we will follow standard practice in the bootstrap
literature and assume that $B_1$ is large enough that it can be ignored and
define $\hat\Delta = \plim_{B_1 \to \infty} \hat\Delta_{B_1}$

@@

\begin{lemma}\label{L1}
  Under Assumptions~\ref{A1} and~\ref{A3},
  $\hat\Delta = \E \hat\tau - \tau + o_p()$.
\end{lemma}

@@

\begin{algorithm}[Confidence intervals]\label{Alg2}
  Define $I^-$, $I^+$, $M^-$, and $M^+$ as in Algorithm~\ref{Alg1}.
  \begin{enumerate}
  \item Estimate the local polynomials $g_{p+1}^+$ and $g_{p+1}^-$ as defined by
    Equation --- and define the residuals
    \begin{equation}
      \label{eq:6}
      \hat\varepsilon_i =
      \begin{cases}
        Y_i - \hat g_{p+1}^-(X_i) & \textif\ X_i < 0 \\
        Y_i - \hat g_{p+1}^+(X_i) & \otherwise
      \end{cases}
    \end{equation}
  \item Repeat the following steps $B_2$ times to produce a sequence of bootstrap
    estimates $\hat\tau_1^{\prime*},\dots,\hat\tau_B^{\prime*}$. For the $k$th step:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M^-(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^-(b_n)\}$ and one of size $M^+(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^+(h_n)\}$. Let $\varepsilon_i^{*-}$ and
      $\varepsilon_i^{*+}$ denote the $i$th element of each sample and construct
      \begin{align}
        \label{eq:2}
        Y_i^{*-} &= \hat g_{p+1}^-(X_i^{*-}) + \varepsilon_i^{*-} &
        Y_i^{*+} &= \hat g_{p+1}^+(X_i^{*+}) + \varepsilon_i^{*+}
      \end{align}
    \item Calculate $\hat\mu_+^*$ and $\hat\mu_-^*$ as
      \begin{align}
        \hat\mu_-^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^-(h_n)} (Y_i^{*-} -
          (\beta_0 + \beta_1 X_i^{*-} + \cdots + \beta_p (X_i^{*-})^p))^2 \\
        \hat\mu_+^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^+(h_n)} (Y_i^{*+} -
          (\beta_0 + \beta_1 X_i^{*+} + \cdots + \beta_p (X_i^{*+})^p))^2
      \end{align}
    \item Apply Algorithm~\ref{Alg1} to the bootstrapped data set,
      \begin{equation*}
        (Y_1^{*-}, X_1^{*-}),\dots,(Y_{M^-(b_n)}^{*-},X_{M^-(b_n)}^{*-}),
        (Y_1^{*+}, X_1^{*+}),\dots,(Y_{M^+(b_n)}^{*+},X_{M^+(b_n)}^{*+}),
      \end{equation*}
      using the same bandwidths $h_n$ and $b_n$ that are used in the rest of
      this algorithm but reestimating all of the local polynomials on the
      bootstrap data. Let $\hat\Delta^*$ represent the bias estimate returned
      by Algorithm~\ref{Alg1}.
    \item Save the bias-corrected estimate
      $\hat\mu_+^* - \hat\mu_i^* - \hat\Delta^*$ as $\hat\tau_k^{\prime*}$.
    \end{enumerate}
  \item Define the confidence interval endpoints $\hat\ell(\alpha)$ and
    $\hat u(\alpha)$ as the $\alpha/2$ and $1-\alpha/2$ quantiles of the
    empirical CDF of $\hat\tau_1^{\prime*},\dots,\hat\tau_{B_2}^{\prime*}$.
  \end{enumerate}
\end{algorithm}

As earlier, we assume that $B_1$ and $B_2$ are large enough that simulation
error can be ignored. Define the limiting values
\begin{align*}
\hat\Delta^* &= \plim_{B_1,B_2 \to \infty} \hat\Delta^*_{B_1,B_2} \\
\hat\ell^*(\alpha) &= \plim_{B_1,B_2 \to \infty} \hat\ell^*_{B_1,B_2}(\alpha) \\
\hat u^*(\alpha) &= \plim_{B_1,B_2 \to \infty} \hat u^*_{B_1,B_2}(\alpha).
\end{align*}
Two results follow. The first is that the secondary bootstrap step produces
a consistent estimator of the bias under the bootstrap distribution. The
second is that the intervals overall are asymptotically valid.

\begin{lemma}\label{L2}
  Under Assumptions~\ref{A1} and~\ref{A3},
  $\hat\Delta^* = \E^* \hat\tau^* - \tau^* + o_{p^*}(-)$.
\end{lemma}

>>>>

\begin{assumption}[Bandwidth]\label{A3}
  Let $h_n$ be the bandwidth used to estimate the local polynomial of
  order $p$ and let $b_n$ be the bandwidth used for $p+1$. Then
  $h_n = o(n^{-1/5})$, $b_n = o(n^{-1/5})$, $n h_n \to \infty$, and
  $n b_n \to \infty$ as $n \to \infty$.\footnote{%
    Unless otherwise stated, all limits in this paper are assumed to
    hold as $n \to \infty$.} %
  The relationship $h_n \leq b_n$ also holds for all $n$.
\end{assumption}

@@

\begin{algorithm}[Bias estimation]\label{Alg1}
  Assume $h_n$ and $b_n$ are bandwidths as described by Assumption~\ref{A3} and
  define
  \begin{align}
    I^-(h) &= \{i : h < X_i < 0\}, &
    I^+(h) &= \{i : 0 < X_i < h\}.
  \end{align}
  Also define $M^-(h_n)$ and $M^+(h_n)$ to be the number of elements in
  $I^-(h_n)$ and $I^+(h_n)$ respectively.
  \begin{enumerate}
  \item Estimate the local polynomials $g_{p+1}^+$ and $g_{p+1}^-$ as defined by
    Equation --- and define the residuals
    \begin{equation}
      \label{eq:1}
      \hat\varepsilon_i =
      \begin{cases}
        Y_i - \hat g_{p+1}^-(X_i) & \textif\ X_i < 0 \\
        Y_i - \hat g_{p+1}^+(X_i) & \otherwise
      \end{cases}
    \end{equation}
  \item Repeat the following steps $B_1$ times to produce a sequence of bootstrap
    estimates $\hat\tau_1^*,\dots,\hat\tau_{B_1}^*$. For the $k$th step:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M^-(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^-(b_n)\}$ and one of size $M^+(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^+(h_n)\}$. Let $\varepsilon_i^{*-}$ and
      $\varepsilon_i^{*+}$ denote the $i$th element of each sample and construct
      \begin{align}
        \label{eq:2}
        Y_i^{*-} &= \hat g_{p+1}^-(X_i^{*-}) + \varepsilon_i^{*-} &
        Y_i^{*+} &= \hat g_{p+1}^+(X_i^{*+}) + \varepsilon_i^{*+}
      \end{align}
    \item Calculate $\hat\mu_+^*$ and $\hat\mu_-^*$ as
      \begin{align}
        \hat\mu_-^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^-(h_n)} (Y_i^{*-} -
          (\beta_0 + \beta_1 X_i^{*-} + \cdots + \beta_p (X_i^{*-})^p))^2 \\
        \hat\mu_+^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^+(h_n)} (Y_i^{*+} -
          (\beta_0 + \beta_1 X_i^{*+} + \cdots + \beta_p (X_i^{*+})^p))^2
      \end{align}
    \item Save $\hat\mu_+^* - \hat\mu_-^*$ as $\hat\tau^*_k$.
    \end{enumerate}
  \item Estimate the bias as
    \begin{equation}
      \label{eq:4}
      \Delta^* = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k -
      \big[\hat g_{p+1}^+(0) - \hat g_{p+1}^-(0)\big]
    \end{equation}
  \end{enumerate}
\end{algorithm}
Obviously, the distribution of $\Delta^*$ depends on $B_1$ and we could
incorporate that dependency into our notation by wrting
$\Delta^*_{B_1}$. However, we will follow standard practice in the bootstrap
literature and assume that $B_1$ is large enough that it can be ignored and
define $\Delta^* = \plim_{B_1 \to \infty} \Delta^*_{B_1}$

@@

\begin{lemma}\label{L1}
  Under Assumptions~\ref{A1} and~\ref{A3},
  $\Delta^* = \E \hat\tau - \tau + o_p()$.
\end{lemma}

@@

\begin{algorithm}[Confidence intervals]\label{Alg2}
  Define $I^-$, $I^+$, $M^-$, and $M^+$ as in Algorithm~\ref{Alg1}.
  \begin{enumerate}
  \item Estimate the local polynomials $g_{p+1}^+$ and $g_{p+1}^-$ as defined by
    Equation --- and define the residuals
    \begin{equation}
      \label{eq:6}
      \hat\varepsilon_i =
      \begin{cases}
        Y_i - \hat g_{p+1}^-(X_i) & \textif\ X_i < 0 \\
        Y_i - \hat g_{p+1}^+(X_i) & \otherwise
      \end{cases}
    \end{equation}
  \item Repeat the following steps $B_2$ times to produce a sequence of bootstrap
    estimates $\hat\tau_1^{\prime*},\dots,\hat\tau_B^{\prime*}$. For the $k$th step:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M^-(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^-(b_n)\}$ and one of size $M^+(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^+(h_n)\}$. Let $\varepsilon_i^{*-}$ and
      $\varepsilon_i^{*+}$ denote the $i$th element of each sample and construct
      \begin{align}
        \label{eq:2}
        Y_i^{*-} &= \hat g_{p+1}^-(X_i^{*-}) + \varepsilon_i^{*-} &
        Y_i^{*+} &= \hat g_{p+1}^+(X_i^{*+}) + \varepsilon_i^{*+}
      \end{align}
    \item Calculate $\hat\mu_+^*$ and $\hat\mu_-^*$ as
      \begin{align}
        \hat\mu_-^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^-(h_n)} (Y_i^{*-} -
          (\beta_0 + \beta_1 X_i^{*-} + \cdots + \beta_p (X_i^{*-})^p))^2 \\
        \hat\mu_+^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^+(h_n)} (Y_i^{*+} -
          (\beta_0 + \beta_1 X_i^{*+} + \cdots + \beta_p (X_i^{*+})^p))^2
      \end{align}
    \item Apply Algorithm~\ref{Alg1} to the bootstrapped data set,
      \begin{equation*}
        (Y_1^{*-}, X_1^{*-}),\dots,(Y_{M^-(b_n)}^{*-},X_{M^-(b_n)}^{*-}),
        (Y_1^{*+}, X_1^{*+}),\dots,(Y_{M^+(b_n)}^{*+},X_{M^+(b_n)}^{*+}),
      \end{equation*}
      using the same bandwidths $h_n$ and $b_n$ that are used in the rest of
      this algorithm but reestimating all of the local polynomials on the
      bootstrap data. Let $\Delta^{**}$ represent the bias estimator returned
      by Algorithm~\ref{Alg1}.
    \item Save the bias-corrected estimator
      $\hat\tau_k^{\prime*} = \hat\mu_+^* - \hat\mu_i^* - \Delta^{**}$.
    \end{enumerate}
  \item Define the confidence interval endpoints $\hat\ell(\alpha)$ and
    $\hat u(\alpha)$ as the $\alpha/2$ and $1-\alpha/2$ quantiles of the
    empirical CDF of $\hat\tau_1^{\prime*},\dots,\hat\tau_{B_2}^{\prime*}$.
  \end{enumerate}
\end{algorithm}

As earlier, we assume that $B_1$ and $B_2$ are large enough that simulation
error can be ignored. Define the limiting values
\begin{align*}
\Delta^{**} &= \plim_{B_1,B_2 \to \infty} \Delta^{**}_{B_1,B_2} \\
\hat\ell^*(\alpha) &= \plim_{B_1,B_2 \to \infty} \hat\ell^*_{B_1,B_2}(\alpha) \\
\hat u^*(\alpha) &= \plim_{B_1,B_2 \to \infty} \hat u^*_{B_1,B_2}(\alpha).
\end{align*}
Two results follow. The first is that the secondary bootstrap step produces
a consistent estimator of the bias under the bootstrap distribution. The
second is that the intervals overall are asymptotically valid.

\begin{lemma}\label{L2}
  Under Assumptions~\ref{A1} and~\ref{A3},
  $\Delta^{**} = \E^* \hat\tau^* - \tau^* + o_{p^*}(-)$.
\end{lemma}
